\documentclass{article}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{automata,positioning}
% \usepackage[margin=0.5in]{geometry}
%\usepackage{fullpage}


\title{Neural Network Computing\\Homework 5}
\author{Liang Niu\\N19486574\\ln932@nyu.edu}

\begin{document}

  % Title Page
  \maketitle % Creates the titlepage
  %\pagenumbering{gobble} % Turns off page numbering
  %\newpage % Starts a new page
  \pagenumbering{arabic} % Turns on page numbering

  % Body
  \section{Program}
  \subsection{Source Code}
    %\paragraph{(a)}
    SOURCE CODE (Python 2.7, numpy needed, anaconda recommended):
    \lstinputlisting[language=Python]{am.py}
  \subsection{Some Explaination}
  \paragraph{Run Environment}
  I also included a source file of my program in the zipped file. If you want to
  run it, please make sure that you have numpy installed. I am using Python 2.7
  in this project. Also Anaconda is highly recommended.
  \paragraph{Parameters}
  There are some parameters in this program that one can adjust to see the
  result. I put them on the begining of the source code and make sure they are
  well commented so that you can know the meaning for every parameter. 
  \paragraph{Toggle}
  There are three main questions so there are three corresponding parts in the
  ``main'' part of the program. And before every part, there is a ``if''
  statement to let you decide whether you want to run this part. Every part is
  indepent with each other. By default, they will all run.
  \paragraph{Run Time}
  On my machine(Macbook Pro 13, early 2015), the prgram need about half a
  minute to finish. This may be different from 10s to 5m I guess.
  \paragraph{Others}
  Because the output will be a lot, I suggest to use the following command to
  redirect the output:\\
  \begin{lstlisting}[language=Bash]
  python am.py | tee output.txt
  \end{lstlisting}

  \section{Analysis and Answers}
  \subsection{Program}
  I wrote a class called AM to do the job. It can predict in two policies:
  direct predict and predict until we get to a converge or run out of loop
  times. Also you can choose to use w or w0, w is the weight matrix that
  diagonal elements all untouched, w0 is the weight matrix that diagonal
  elements are all set to 0. Which means I implemented 4 kinds of predict
  methods:(direct, w), (direct, w0), (converge, w), (converge, w0). You can see
  in the Q1 part code, I tried all of 4 kinds of prediction.\\
  display() can help to display the patterns for you to recognize.\\
  disturbe() is to help make noise into the data.
  
  \subsection{Q1}
  The output for Q1 is in a manner that ``method,numbers,weight''.\\
  ``method'' maybe direct or converge. Direct means predict just use $w*input$,
  ``converge'' means predict iteratively until converge or reach the maximum
  loop times.\\
  ``numbers'' is the working combination of the patterns.\\
  ``weight'' may be ``p'' or ``p0''. ``p'' means we get this result by using the
  weight matrix with digonal elements stay untouched. ``p0'' means we get this
  result by using the weght matrix with all diagonal elemets set 0.\\
  As we can see, there are 456 kinds of combinations that can be stored and
  retrived smoothly. Thus the maximum capacity of AM in this problem is 5.\\
  The full results of combinations that can be stored is attached.



  \subsection{Q2}
  For this question, I just do the experiments under those patterns that can be
  stored. And I implemented two kinds of noise: the first one is that missing,
  which turn some points in the pattern into 0, the second one is mistake, which
  is to flip some points in the pattern.\\
  Observe the result, we can conclude that:\\
  1. When number of errors increased, error rate increased.\\
  2. When number of patterns stored increased, the number of errors that it can
  tolerate decreased.\\
  3. When error number is big enough, the network will only give out wrong
  result.\\

  \subsection{Q3}
  For this question, I just do the experiments under those patterns that can be
  stored. And I implemented using direct predict with w0. Typically, the
  spurious patterns looks like some of the train patterns very much, just with
  some points flipped or missing. For example, there are some spurious
  patterns(1 is \#, -1 is space, 0 is ?) in the following figure.\\
  \begin{figure}
  \begin{verbatim}
              ###  |  ###  |     #
             #   # | #   # |    ## 
             #   # |    #  |  ?# #
              ?##? |   #   |  #  #
                 # |   #   | #####
                 # |       | ?  ?# 
             ####  | ##### |     # 
             ---------------------
              #### | ##### |  ###
             #   ? | #     | #   #
             #     | #     |     #
             ####  | # ##  |   ##
             #   # |     # |     #
             #   # |     # |     #
              ###  | ####  |  ###
             ---------------------
  \end{verbatim}
  \end{figure}
  In the number 9, some points are missing. In the number 2, some points are
  flipped(from 1 to -1), in the number 4, some points which should be -1 are missing.\\
\end{document}
